A Tutorial on Tailored Simulation-Based Power Analysis for Experimental Designs with Generalized Linear Mixed Models

### 2024-03-13 docs/manuscript.Rmd
move the lme4 package section
minimal work on new marginaleffects code for hypotheses testing

## The lme4 package in R

@@

@@

```{r}
library(marginaleffects)
hypotheses(fit, hypothesis = c(
  "`advice_present` + `advice_correct` + `expert:advice_present` +
  `expert:advice_correct` = 0",
  "`advice_present` + `advice_correct` = 0",
  "`advice_present` + `expert:advice_present` = 0",
  "`advice_present` = 0"
), equivalence = 0)

avg_predictions(fit, variables = list(expert = 0:1, advice_present = 0:1, advice_correct = 0:1)) %>%
  hypotheses(hypothesis = c(
    "b8 - b2 = 0",
    "b7 - b1 = 0",
    "b2 - b4 = 0",
    "b1 - b3 = 0"
    )) %>%
  inferences(method = "delta")

comparisons(fit)
avg_comparisons(fit, hypothesis = c(
  "`advice_present` + `advice_correct` + `expert:advice_present` +
  `expert:advice_correct` = 0",
  "`advice_present` + `advice_correct` = 0",
  "`advice_present` + `expert:advice_present` = 0",
  "`advice_present` = 0"
))
```

@@

>>>>

@@

<!-- ## The lme4 package in R -->

@@

@@

We can specify and test hypothesis like these with the marginaleffects [@R-marginaleffects] package.

```{r}
library(marginaleffects)

hypotheses(fit, hypothesis = c(
  "`advice_present` + `advice_correct` + `expert:advice_present` +
  `expert:advice_correct` = 0",
  "`advice_present` + `advice_correct` = 0",
  "`advice_present` + `expert:advice_present` = 0",
  "`advice_present` = 0"
), equivalence = 0)

hypotheses(fit, hypothesis = c(
  "`advice_present` + `advice_correct` + `expert:advice_present` +
  `expert:advice_correct` = 0",
  "`advice_present` + `advice_correct` = 0",
  "-1 * (`advice_present` + `expert:advice_present`) = 0",
  "-1 * (`advice_present`) = 0"
), equivalence = 0)
```

## Interval estimation

STILL MISSING
